### 2019-05-06 2-Chapters/3-Chapter/chapter3.tex
SO NOT SURE HOW TO CONTINUE THIS CHAPTER

@@

\begin{itemize}
    \item Algorithm 1 is
    an $\varepsilon$-greedy algorithm, as described in \cite{Bubeck12}, using $\varepsilon_t = \varepsilon_0 / t$, and $\varepsilon_0 = 0.1$ (chosen arbitrarily) (\texttt{EpsilonDecreasing}).

    \item Algorithm 2 is
    an Explore-then-Commit algorithm from \cite{GarivierETC2016}, that knows the horizon, and a lower-bound on the gap between arms (chosen arbitrarily as $\delta=0.01$, valid for all problems) (\texttt{ETC\_KnownGap}).

@@

% FIXME update if needed?
We consider increasing values for the horizon, $T=1000$, $T=2500$, $T=5000$, $T=10000$, $T=20000$, $T=25000$ and $T=50000$.
We consider as well an increasing number of arms, $K=2$, $K=4$, $K=8$, $K=12$, $K=16$, $K=20$ and $K=32$.
For all experiments, we run $N=100$ independent simulations.

@@

\TODOL{FIXME launch these experiments, for a very short number of repetitions N=4, and if I'm happy about the results and if they are easily copied-and-pasted here, then launch with N=100 or N=1000 depending on the running time of the whole simulations}

@@

@@

@@

>>>>

% \TODOL{Write text for this Section, write configuration.py file, run short-term experiment, include them, if happy about it, run longer ang larger experiments}

@@

\begin{itemize}
    \item Algorithm 1 is
    an $\varepsilon$-greedy algorithm, as described in \cite{Bubeck12}, using $\varepsilon_t = \varepsilon_0 / t$, and $\varepsilon_0 = 0.1$ (chosen arbitrarily) (\texttt{EpsilonDecreasing}).
    It has a very small cost in terms of time and memory, but it usually achieves linear regret.

    \item Algorithm 2 is
    an Explore-then-Commit algorithm from \cite{GarivierETC2016}, that knows the horizon, and a lower-bound on the gap between arms (chosen arbitrarily as $\delta=0.01$, valid for all problems) (\texttt{ETC\_KnownGap}).
    Similarly to $\varepsilon$-greedy, it has a very small footprint in terms of time and memory, but only obtain large (linear) regret.

@@

% FIXME update if needed?
We consider increasing values for the horizon, and we focus on $7$ exponentially-spaced values: $T=1000$, $T=2500$, $T=5000$, $T=10000$, $T=20000$, $T=25000$ and $T=50000$.
We consider as well an increasing number of arms, and we focus again on $7$ values: $K=2$, $K=4$, $K=8$, $K=12$, $K=16$, $K=20$ and $K=32$.
For all experiments, we run $N=100$ independent simulations.

@@

% \TODOL{FIXME launch these experiments, for a very short number of repetitions N=4, and if I'm happy about the results and if they are easily copied-and-pasted here, then launch with N=100 or N=1000 depending on the running time of the whole simulations}

@@

\paragraph{Normalizing data?}

The two figures below regret normalized data, in the following way.
For each algorithm, we ran simulations to obtain its (empirical) regret, computation time and space requirement, for different problems with different values of $K$ and $T$.
Simply considering the average of such measurements make no sense, as for instance two values of the regret for $T=1000$ or $T=50000$ do not have the same order of magnitude.
%
We know that efficient algorithms are expected to follow these patterns:
\begin{itemize}
    \item Final regret $R_T$ should scale as $\cO(K \log(T))$,
    \item Total computation time $\cT_T$ should scale as $\cO(K T)$ (\ie, a computation time of $\cO(K)$ for each time step $t$),
    \item Total memory cost should scale $\cM_T$ as $\cO(K \log(T))$.
\end{itemize}
Thus, we normalized the data by dividing the regrets by $K \log(T)$, the times by $K T$ and the memory by $K$.

@@

\begin{figure}[h!]  % [htbp]
	% \centering
	\includegraphics[width=1.05\linewidth]{16_different_algorithms__lognormregret_vs_lognormtime__56pb__7KS_7Ts.pdf}
	\caption[Normalized mean regret vs normalized running time (in micro-seconds).]{
        Normalized mean regret vs normalized running time (in micro-seconds),
        aggregating the results from different values of $K$ and $T$, for $16$ algorithms.
        Both the $x$-axis and $y$-axis are in log-scale.
        \UCB{} and \klUCB{} are among the best algorithms, while AdBandits, Thompson sampling and Bayes-UCB slightly outperform them in terms of regret, and have similar running times.
	}
	\label{fig:3:16_different_algorithms__lognormregret_vs_lognormtime__56pb__7KS_7Ts}
\end{figure}

@@

\begin{figure}[h!]  % [htbp]
	% \centering
	\includegraphics[width=1.05\linewidth]{16_different_algorithms__lognormregret_vs_lognormmemory__56pb__7KS_7Ts.pdf}
	\caption[Normalized mean regret vs normalized memory costs (in bytes).]{
        Normalized mean regret vs normalized memory costs (in bytes),
        aggregating the results from different values of $K$ and $T$, for $16$ algorithms.
        Both the $x$-axis and $y$-axis are in log-scale.
        Thompson sampling appears as the best algorithm in this visualization, while \UCB{} has the advantage of being memory efficient, and \klUCB{} obtains similar performances.
	}
	\label{fig:3:16_different_algorithms__lognormregret_vs_lognormmemory__56pb__7KS_7Ts}
\end{figure}
